Parallelization of Push-based System for Molecular Simulation Data Analysis

### 2016-01-21 paper/paperSource.tex
Paper

\documentclass[10pt,journal,final,letterpaper,twocolumn,conference]{IEEEtran}
%\documentclass{ssdbm}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{algorithmic,amsfonts,amssymb,amsmath,calc,calrsfs,cleveref}
\usepackage{epstopdf,filecontents,lipsum}
%\usepackage{fixltx2e}

@@

In various sciences simulation systems take big place and often times they may be very important for results. One of such sciences, which is primarily related to this paper, is physics. In this case, from computer engineering point of view, simulations generally have the following flow:

@@

\bibliographystyle{IEEEtran}
\bibliography{references.bib}

>>>>

\documentclass[10pt,journal,final,letterpaper,twocolumn]{IEEEtran}
%\documentclass{ssdbm}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{algorithmic,amsfonts,amssymb,amsmath,calc,calrsfs,cleveref}
%\usepackage{fixltx2e}

@@

In various sciences simulation systems take big place and often times they may be very important for results. One of such sciences, which is primarily related to this paper, is physics. In this case, from computer engineering point of view, simulations generally have the following flow \cite{mainPaper}:

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
